* Smth Interesting
** Church "\lambda-calculus"
** Gödel "recursive functions"
** Turing "Turing Machine"

* 1098
** Russel "Mathematics logic base on theory of types"
** Curry "paradox"
** Hensen "Simply-typed \lambda-calculus

* Propositions as Types
** Proof -> Programs

* Exercises
** Equivalence
1) b
2) c
3) b
** Combinators
1) T
2) F
3) T
4) T
5) Fn
** ß - NF?
1) T
2) F
3) T

** Eval
1) (λabc.cba)zz(λwv.w) -> (λwv.w)zz -> z
2) (λx.λy.xyy)(λa . a)b -> (λa.a)bb -> bb
3) (λy.y)(λx.xx)(λz.zq) -> (λz.zq)(λz.zq) -> (λz.zq)q -> qq
4) yy
5) (λx.λy.xyy)(λy.y)y -> (λy.y)yy -> yy
6) (λa.aa)(λb.ba)c -> (λb.ba)(λb.ba)c -> (λb.ba)ac -> aac
7) (λxyz.xz(yz))(λx.z)(λx.a) -> (λxym.xm(ym))(λx.z)(λx.a) ->
   (λm.(λx.z)m((λx.a)m)) ->
   (λm.za)

* Additional task
** Parentheses
   1) λx. x z λy. x y
      (λx. ((x z) (λy. (x y))))

   2) (λx. x z) λy. w λw. w y z x
      ((λx. (x z)) (λy. (w (λw. ((((w y) z) x)))))

   3) λx. x y λx. y x
      (λx. ((x y) (λx. (y x))))

** Free variables
   Identify all the free variables in the following expressions.
   1) λx. x z λy. x y
      (λx. ((x _z_) (λy. (_x_ y))))

   2) (λx. x z) λy. w λw. w y z x
      (λx. (x _z_)) (λy. ((_w_) (λw. ((((w y) _z_) _x_)))))

   3) λx. x y λx. y x
      λx. ((x _y_) (λx. (_y_ x)))
** β-reduction
   Reduce the following expressions as much as possible.
   1. (λx. x λy. λz. z y x)(y z)
      (λx. (x λy. λz. ((z y) x)))(y z)
      (λx. ((y z) λy. λz1. ((z1 y) (y z))))
      yz (λy1. λz1. z1 y1 yz)

   2. (λn. λf. λx. f(n f x))(λx. λf. x x x x f)
      λf1. λx1. f1(λx. λf. (x x x x f) f1 x1)
      λf1. λx1. f1 (f1 f1 f1 f1 x1)
      λfx. f f f f f x

   3. (λx. x(λx. λy. y)(λy. λx. y))(λx. λy. y)
      (λx. λy. y)(λx. λy. y)(λy. λx. y)
      λy. λx. y

   // Error in the repo. missed one y1
   4. (λx. λy. xy)(λz. (λc. y) z)
      λy1. ((λz. (λc. y) z) y1)
      λy1. ((λc. y) y1)
      λy1. y

   5. (λx. λy. x y)(λz. (λc. c y) z)

   6. (λx. x q)(λy. y y y)
   7. (λc. c(λx. (λx. λy. y))(λx. λy. x))(λq. q)
   8. (λz. z)(λy. y y)(λx. x a)
   9. (λz. z)(λz. z z)(λz. z y)
   10. (λx. λy. x y y)(λa. a) b
   11. (λx. λy. x y y)(λy. y) y
   12. (λx. x x)(λy. y x) z
   13. (λx. (λy. (x y)) y) z
   14. ((λx. x x)(λy. y))(λy. y)
   15. (((λx. λy. (x y))(λy. y)) w)
   16. (λx. y)((λy. y y y)(λx. x x x))
